---
title: "Digital Health-Seeking Behaviors Tables"
author: "Adam Northrup, Data Manager, ETAC"
date: "June 19, 2019"
output: html_document
---
```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
                      warning = FALSE, message = FALSE)
#####Read libraries
library(tidyverse)
library(sjlabelled)
library(rio)
library(openxlsx)
library(scales)
library(kableExtra)

#####Load data
# setwd("C:/Users/anorthrup/Box Sync/ETAC")
load("acasi.RData")
source("DHSB Table Functions.R")
```

```{r}
#####Print "Other" text for each demographic variable
# wb <- createWorkbook()
# for (i in c("GENDERS", "RACEFS", "ORIENTS", "LIVED6LS", "STAY7DS", 
#            "INSUREHS", "SSNDOS", "CNEED3ES", "DISCJS")) {
#   addWorksheet(wb, i)
#   writeData(wb, i, acasi %>%
#               select(SITE1, PID, i) %>%
#               filter(!!sym(i) != "[Skipped]"))
# }
# saveWorkbook(wb, "ACASI Other Text.xlsx", overwrite = TRUE)

#####Format variables and rename
demo <- acasi %>%
  filter(Set == 1) %>% #Remove participants without 06m assessment
  filter(!(is.na(HE_RC_HAL) | is.na(HE_RC_HSE))) %>%
  filter(AGE >= 18) %>%
  select(-RACE, -starts_with("S56")) %>%
  filter(!(is.na(HE_RC_HSE) | is.na(HE_RC_HAL))) %>%
  mutate(`Age Groups` = as.factor(case_when(AGE < 25 ~ "18-24 Years",
                                            AGE >= 25 ~ "25-34 Years")),
         SCREEN5 = fct_recode(as.factor(SCREEN5),
                              "Within past 12 months" = "1", "More than 12 months ago" = "2",
                              "Don't know"   = "7", "Refuse to answer"        = "8"),
         ViralSupp_MCD = fct_recode(as.factor(ViralSupp_MCD),
                                    "Not suppressed" = "0",
                                    "Suppressed"     = "1"),
         DISC_RC = if_else(DISCA == 0, "Disclosed", "Did not disclose"),
         DRUG_RCD_None = if_else(DRUG1LM == 1 & DRUG2LK == 1, 1, 0)) %>%
  # mutate_at(vars(matches("(CARE)([[:alpha:]]+)(\\d+)")),
  #           list(~as.factor(case_when(. == 0  ~ "No",
  #                                     . <= 98 ~ "Yes",
  #                                     . >= 98 ~ "Missing")))) %>%
  mutate(INJECTL_RC = case_when(INJECTL == 1 ~ "Injected drugs",
                                INJECTL == 0 ~ "Did not inject drugs")) %>%
  unite("SitePID", SITE_RC, PID, remove = FALSE) %>%
  arrange(SITE_RC, PID) %>%
  mutate_at(vars(matches("DISC_RCD|DRUG_RCD")), list(~as.numeric(as.character(.))))
```

```{r}
#####Number of participants
newNames <- bind_rows(
  demo %>%
    summarize(Frequency = n()) %>%
    mutate(SITE_RC = "Overall_1"),
  demo %>%
    group_by(SITE_RC) %>%
    summarize(Frequency = n()) %>%
    mutate(SITE_RC = as.character(SITE_RC))
) %>%
  unite("NewNames", SITE_RC, Frequency, sep = " (N=", remove = FALSE) %>%
  mutate(NewNames = str_c(NewNames, ")")) %>%
  select(-Frequency) %>%
  mutate(NewNames = factor(NewNames, levels = unique(NewNames))) %>%
  spread(NewNames, SITE_RC) %>%
  unlist()
#####Table 1: participant characteristics summary
table1 <- bind_rows(
  #Age groups
  table_OneFactor(demo, varString = "Age Groups",
                  varRelevel = c("18-24 Years")),
  #Ethnicity/Race
  table_OneFactor(demo, varString = "RACE_RC", header = "Ethnicity and Race", 
                  varRelevel = c("Latino",
                                 "Black, Not Latino",
                                 "White, Not Latino",
                                 "White Mixed-Race, Not Latino or Black")),
  #Gender
  table_OneFactor(demo, varString = "GENDER_RC", header = "Gender Identity",
                  varRelevel = c("Male (cis man)",
                                 "Female (cis woman)",
                                 "Trans-identified")),
  #Orientation
  table_OneFactor(demo, varString = "ORIENT_RC", header = "Sexual Orientation",
                  varRelevel = c("Straight",
                                 "Gay or lesbian",
                                 "Bisexual")),
  #Education
  table_OneFactor(demo, varString = "GRADE_RC", header = "Education",
                  varRelevel = c("High school, equivalent or less",
                                 "Some post-K12")),
  #Residence
  table_OneFactor(demo, varString = "STAY7D_RC", 
                  header = "Current Residence",
                  varRelevel = c("Stable housing")),
  #Income
  table_Continuous(demo, variable = "MONEY_RC", stat = "median", 
                   name = "Monthly Income",
                   header = "Monthly Income")
) %>%
  mutate(Variable = str_replace(Variable, "(Monthly Income)(.*)", "\\1")) %>%
  mutate(Overall = str_replace(Overall, "(\\d+)(/\\d+)(.*)", "\\1\\3")) %>%
  mutate_at(vars(-Header, -Variable, -Overall),
            list(~str_replace(., "(.*)(\\d \\()(.*)(%\\)$)", "\\3"))) %>%
  mutate_at(vars(-Header, -Variable, -Overall),
            list(~str_replace(., "(\\d+)( \\[.*\\]$)", "\\1"))) %>%
  separate(Overall, c("Overall_1", "Overall_2"), sep = " ") %>%
  mutate(Overall_2 = str_replace(Overall_2, "(\\()(.*)(%\\))", "\\2")) %>%
  add_row(Header = "Characteristic (Categorical)", 
          Variable = "Characteristic (Categorical)", 
          .before = 1) %>%
  mutate(Overall_1 = replace(Overall_1, 
                             which(Variable == "Characteristic (Categorical)"),
                             "n")) %>%
  mutate_at(vars(-Header, -Variable, -Overall_1), list(~replace(., 1, "%"))) %>%
  mutate_at(vars(Header, Variable), list(~str_remove(., ", N \\(%\\)"))) %>%
  mutate_at(vars(Header, Variable), list(~str_remove(., ", Median \\[IQR\\]"))) %>%
  add_row(.before = nrow(.) - 1, 
          Header = "Characteristic (Continuous)",
          Variable = "Characteristic (Continuous)") %>%
  mutate(Overall_2 = replace(Overall_2, 
                             which(Variable == "Characteristic (Continuous)"),
                             "IQR")) %>%
  mutate_at(vars(-Header, -Variable, -Overall_2), 
            list(~replace(., which(Variable == "Characteristic (Continuous)"), "med"))) %>%
  rename(!!newNames) %>%
  add_row(Variable = "STAY7D_RC: Six participants in 'Institution' (hospital or prison) were incorporated into 'Unstable housing'.") %>%
  add_row(Variable = paste0("Monthly income overall sample size N=", length(which(!is.na(demo$MONEY_RC))), " due to response of Don't Know/Not Sure"))

#####Table 2: participant health care summary
table2 <- bind_rows(
  bind_rows(
    #HIV Diagnosis
    table_OneFactor(demo, varString = "SCREEN5", header = "HIV Diagnosis",
                    varRelevel = c("Within past 12 months",
                                   "More than 12 months ago")),
    #Viral Suppression
    table_OneFactor(demo, varString = "ViralSupp_MCD",
                    header = "Viral Suppression") %>%
      filter(Variable != "   Not suppressed"),
    #Insurance
    table_OneFactor(demo, varString = "INSURE_RC", header = "Insurance"),
    #Health care history, 6 months
    bind_rows(
      table_OneFactor(demo, varString = "CARED6_RC", 
                      header = "Recent Health Care") %>%
        filter(Variable != "   No") %>%
        mutate(Variable = replace(Variable, str_which(Variable, "Yes"), 
                                  "   Doctor's visit, non-HIV, 6 months")),
      table_OneFactor(demo, varString = "CAREHV06_MCD_RC", 
                      header = "Recent Health Care") %>%
        filter(str_detect(Variable, "Yes")) %>%
        arrange(desc(Variable)) %>%
        mutate(Variable = replace(Variable, str_which(Variable, "Yes"), 
                                  "   Doctor's visit, HIV, 6 months"))
    ),
    #HIV Disclosure
    table_OneFactor(demo, varString = "DISC_RC", 
                    header = "HIV Disclosure Status") %>%
      filter(Variable != "   Did not disclose"),
    #Substance Use
    bind_rows(
      table_ManyBinary(demo, header = "Substance Use",
                       variables = c(
                         "DRUG_RCD_None"      = "None",
                         "DRUG_RCD_Alcohol"   = "Alcohol",
                         "DRUG_RCD_Tobacco"   = "Tobacco",
                         "DRUG_RCD_Marijuana" = "Marijuana",
                         "DRUG_RCD_Other"     = "Other non-injected drug(s)"
                       )),
      table_OneFactor(demo, varString = "INJECTL_RC", header = "Substance Use") %>%
        filter(Variable == "   Injected drugs")
    )
  ) %>%
    mutate_at(vars(-Header, -Variable, -Overall),
              list(~str_replace(., "(.*)(\\d \\()(.*)(%\\)$)", "\\3"))) %>%
    separate(Overall, c("Overall_1", "Overall_2"), sep = " ") %>%
    mutate(Overall_2 = str_replace(Overall_2, "(\\()(.*)(%\\))", "\\2")) %>%
    add_row(Header = "Characteristic (Categorical)", 
            Variable = "Characteristic (Categorical)", 
            .before = 1) %>%
    mutate(Overall_1 = replace(Overall_1, 
                               which(Variable == "Characteristic (Categorical)"),
                               "n")) %>%
    mutate_at(vars(-Header, -Variable, -Overall_1), list(~replace(., 1, "%"))),
  bind_rows(
    #Youth Health Engagement
    #> Health Access Literacy
    table_Continuous(demo, variable = "HE_RC_HAL",
                     name = "Health Access Literacy", 
                     header = "Youth Health Enagement"),
    #> Health Self-Efficacy
    table_Continuous(demo, variable = "HE_RC_HSE", 
                     name = "Health Self-Efficacy",
                     header = "Youth Health Enagement"),
    #Provider Empathy
    table_Continuous(demo, variable = "CARE_RC",
                     name = "Provider Empathy", 
                     header = "Provider Empathy"),
    #Social Support
    table_Continuous(demo, variable = "SOCIALS_RC",
                     name = "Social Support", 
                     header = "Social Support"),
    #HIV-Related Stigma
    table_Continuous(demo, variable = "STIGMA_RC",
                     name = "HIV-Related Stigma", 
                     header = "HIV-Related Stigma"),
    #Physical and Mental Health
    table_Continuous(demo, variable = "MENTALH_RC",
                     name = "Mental Health",
                     header = "Physical and Mental Health")
    # table_Continuous(demo, variable = "MENTALH4",
    #                  name = "Mental and Physical Health, 1 item")
  ) %>%
    mutate_at(vars(-Header, -Variable, -Overall),
              list(~str_replace(., "(.*)(\\d+)( \\(.*\\)$)", "\\1\\2"))) %>%
    separate(Overall, c("Overall_1", "Overall_2"), sep = " ") %>%
    add_row(Header = "Characteristic (Scale)", 
            Variable = "Characteristic (Scale)", 
            .before = 1) %>%
    mutate(Overall_2 = replace(Overall_2, 
                               which(Variable == "Characteristic (Scale)"),
                               "(SD)")) %>%
    mutate_at(vars(-Header, -Variable, -Overall_2), list(~replace(., 1, "m")))
) %>%
  mutate(Overall_1 = str_replace(Overall_1, "(\\d+)(/\\d+)", "\\1")) %>%
  mutate_at(vars(Header, Variable), list(~str_remove(., ", N \\(%\\)"))) %>%
  mutate_at(vars(Header, Variable), list(~str_remove(., ", Mean \\(SD\\)"))) %>%
  rename(!!newNames) %>%
  add_row(Variable = paste0("Viral suppression information obtained from medical chart data (N=",
          length(which(demo$ViralSupp_MCD_RC != "Missing")), ")")) %>%
  add_row(Variable = paste0("HIV doctor visit information obtained from medical chart data (N=",
          length(which(demo$CAREHV06_MCD_RC != "Missing")), ")")) %>%
  add_row(Variable = paste0("Injected drug information N=",
          length(which(demo$INJECTL_RC != "Missing")), " due to refusals to answer."))
save(table1, table2, file = "Tables Participants.RData")
```

### Table 1
```{r include = TRUE}
table1Index <- table1 %>%
  filter(complete.cases(.)) %>%
  select(Header) %>%
  mutate(Row = row_number()) %>%
  group_by(Header) %>%
  summarize(
    Start = min(Row),
    End   = max(Row)
  ) %>%
  arrange(Start)

kable(table1 %>%
        filter(complete.cases(.)) %>%
        select(-Header),
      caption = 
        paste0("Table 1. Sociodemographic characteristics of young adults living with HIV across 10 demonstration sites in the United States (N = ", nrow(demo), ")")
      ) %>%
  kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  kableExtra::group_rows(table1Index$Header[1], table1Index$Start[1], table1Index$End[1]) %>%
  kableExtra::group_rows(table1Index$Header[2], table1Index$Start[2], table1Index$End[2]) %>%
  kableExtra::group_rows(table1Index$Header[3], table1Index$Start[3], table1Index$End[3]) %>%
  kableExtra::group_rows(table1Index$Header[4], table1Index$Start[4], table1Index$End[4]) %>%
  kableExtra::group_rows(table1Index$Header[5], table1Index$Start[5], table1Index$End[5]) %>%
  kableExtra::group_rows(table1Index$Header[6], table1Index$Start[6], table1Index$End[6]) %>%
  kableExtra::group_rows(table1Index$Header[7], table1Index$Start[7], table1Index$End[7]) %>%
  kableExtra::group_rows(table1Index$Header[8], table1Index$Start[8], table1Index$End[8]) %>%
  kableExtra::group_rows(table1Index$Header[9], table1Index$Start[9], table1Index$End[9])
```
Footnotes:  

* STAY7D_RC: Six participants in 'Institution' (hospital or prison) were incorporated into 'Unstable housing'.
* Monthly income overall sample size N= `r length(which(!is.na(demo$MONEY_RC)))` due to response of Don't Know/Not Sure.

### Table 2
```{r include = TRUE}
table2Index <- table2 %>%
  filter(complete.cases(.)) %>%
  select(Header) %>%
  mutate(Row = row_number()) %>%
  group_by(Header) %>%
  summarize(
    Start = min(Row),
    End   = max(Row)
  ) %>%
  arrange(Start)

kable(table2 %>%
        filter(complete.cases(.)) %>%
        select(-Header),
      caption = "Table 2. Candidate predictors of digital health seeking, including HIV-related health, healthcare utilization, substance use, and mental health reported at baseline") %>%
  kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  kableExtra::group_rows(table2Index$Header[1], table2Index$Start[1], table2Index$End[1]) %>%
  kableExtra::group_rows(table2Index$Header[2], table2Index$Start[2], table2Index$End[2]) %>%
  kableExtra::group_rows(table2Index$Header[3], table2Index$Start[3], table2Index$End[3]) %>%
  kableExtra::group_rows(table2Index$Header[4], table2Index$Start[4], table2Index$End[4]) %>%
  kableExtra::group_rows(table2Index$Header[5], table2Index$Start[5], table2Index$End[5]) %>%
  kableExtra::group_rows(table2Index$Header[6], table2Index$Start[6], table2Index$End[6]) %>%
  kableExtra::group_rows(table2Index$Header[7], table2Index$Start[7], table2Index$End[7]) %>%
  kableExtra::group_rows(table2Index$Header[8], table2Index$Start[8], table2Index$End[8]) %>%
  kableExtra::group_rows(table2Index$Header[9], table2Index$Start[9], table2Index$End[9]) %>%
  kableExtra::group_rows(table2Index$Header[10], table2Index$Start[10], table2Index$End[10]) %>%
  kableExtra::group_rows(table2Index$Header[11], table2Index$Start[11], table2Index$End[11]) %>%
  kableExtra::group_rows(table2Index$Header[12], table2Index$Start[12], table2Index$End[12]) %>%
  kableExtra::group_rows(table2Index$Header[13], table2Index$Start[13], table2Index$End[13])
```
Footnotes:

* Viral suppression information obtained from medical chart data (N = `r length(which(demo$ViralSupp_MCD_RC != "Missing"))`).
* HIV doctor visit information obtained from medical chart data (N = `r length(which(demo$CAREHV06_MCD_RC != "Missing"))`).
* Injected drug information N = `r length(which(demo$INJECTL_RC != "Missing"))` due to refusals to answer.
```{r eval = FALSE}
wb <- loadWorkbook("DHSB Tables.xlsx")
#Table 1
removeWorksheet(wb, "Table 1")
addWorksheet(wb, "Table 1")
writeData(wb, sheet = "Table 1", table1 %>% select(-Header))
setColWidths(wb, sheet = "Table 1", cols = 1:ncol(table1), widths = "auto")
#Table 2
removeWorksheet(wb, "Table 2")
addWorksheet(wb, "Table 2")
writeData(wb, sheet = "Table 2", table2 %>% select(-Header))
setColWidths(wb, sheet = "Table 2", cols = 1:ncol(table2), widths = "auto")

saveWorkbook(wb, "DHSB Tables.xlsx", overwrite = TRUE)
```

### Testing Across Sites

```{r chisqSites, include = TRUE}
#####Table 1 Chi-Squared testing across sites
#> Create data frame with counts across sites for each variable
tableChisq <- bind_rows(
  #Age groups
  table_OneFactor(demo, varString = "Age Groups",
                  varRelevel = c("18-24 Years")),
  #Ethnicity/Race
  table_OneFactor(demo, varString = "RACE_RC", header = "Ethnicity and Race", 
                  varRelevel = c("Latino",
                                 "Black, Not Latino",
                                 "White, Not Latino",
                                 "White Mixed-Race, Not Latino or Black")),
  #Gender
  table_OneFactor(demo, varString = "GENDER_RC", header = "Gender Identity",
                  varRelevel = c("Male (cis man)",
                                 "Female (cis woman)",
                                 "Trans-identified")),
  #Orientation
  table_OneFactor(demo, varString = "ORIENT_RC", header = "Sexual Orientation",
                  varRelevel = c("Straight",
                                 "Gay or lesbian",
                                 "Bisexual")),
  #Education
  table_OneFactor(demo, varString = "GRADE_RC", header = "Education",
                  varRelevel = c("High school, equivalent or less",
                                 "Some post-K12")),
  #Residence
  table_OneFactor(demo, varString = "STAY7D_RC", 
                  header = "Current Residence",
                  varRelevel = c("Stable housing")),
  #HIV Diagnosis
  table_OneFactor(demo, varString = "SCREEN5", header = "HIV Diagnosis",
                  varRelevel = c("Within past 12 months",
                                 "More than 12 months ago")),
  #Viral Suppression
  table_OneFactor(demo, varString = "ViralSupp_MCD",
                  header = "Viral Suppression"),
  #Insurance
  table_OneFactor(demo, varString = "INSURE_RC", header = "Insurance"),
  #Health care history, 6 months
  table_OneFactor(demo, varString = "CARED6_RC", 
                  header = "Non-HIV Care Visit, 6 Months"),
  table_OneFactor(demo, varString = "CAREHV06_MCD_RC", 
                  header = "HIV Care Visit, 6 Months"),
  #HIV Disclosure
  table_OneFactor(demo, varString = "DISC_RC", 
                  header = "HIV Disclosure Status"),
  #Substance Use
  table_OneFactor(demo, varString = "DRUG_RCD_Alcohol",
                  header = "Substance Use: Alcohol"),
  table_OneFactor(demo, varString = "DRUG_RCD_Tobacco",
                  header = "Substance Use: Tobacco"),
  table_OneFactor(demo, varString = "DRUG_RCD_Marijuana",
                  header = "Substance Use: Marijuana"),
  table_OneFactor(demo, varString = "DRUG_RCD_Other",
                  header = "Substance Use: Other Non-Injected")
) %>%
  mutate(Overall = str_replace(Overall, "(\\d+)(/\\d+)", "\\1")) %>%
  filter(!is.na(Overall)) %>%
  mutate_at(vars(-Header, -Variable), list(~str_remove(., " \\(.*\\)$"))) %>%
  mutate_at(vars(-Header, -Variable), list(~str_remove(., " \\[.*\\]$"))) %>%
  mutate(Header = str_remove(Header, ", N \\(%\\)")) %>%
  mutate_at(vars(-Header, -Variable), list(as.integer))

#> Chi-squared tests
bind_rows(
  chisq.dhsb(table1Chisq, table1Chisq_vars[1]),
  chisq.dhsb(table1Chisq, table1Chisq_vars[2]),
  chisq.dhsb(table1Chisq, table1Chisq_vars[3]),
  chisq.dhsb(table1Chisq, table1Chisq_vars[4]),
  chisq.dhsb(table1Chisq, table1Chisq_vars[5]),
  chisq.dhsb(table1Chisq, table1Chisq_vars[6])
) %>%
  mutate(Warning = c("No", "Yes", "Yes", "Yes", "No", "No")) %>%
  kable(., digits = 3,
        caption = "Chi-Square Testing for Categorical Variables Across Site") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"))

```

```{r anovaSites, include = TRUE}
tableAnova <- acasi %>%
  filter(Set == 1) %>%
  filter(AGE > 17) %>%
  filter(!(is.na(HE_RC_HAL) | is.na(HE_RC_HSE))) %>%
  select(SITE1, MONEY_RC_Log, HE_RC_HAL, HE_RC_HSE, CARE_RC, MENTALH_RC,
         MTUEX_RC, MTUSPX_RC_Text, MTUSPX_RC_Smartphone, MTUIX_RC,
         MTUSNX_RC, MTUAX_RC_Pos, MTUAX_RC_Anx, MTUAX_RC_Neg)

anova.dhsb(tableAnova) %>%
  left_join(
    .,
    acasi_labels,
    by = "Variable"
  ) %>%
  mutate(Label = replace(Label, which(Variable == "MONEY_RC_Log"), "Log Monthly Income")) %>%
  mutate(
    Table = NA,
    Table = replace(Table, str_which(Label, "MTUAS"), "Table 3"),
    Table = replace(Table, which(Label == "Log Monthly Income"), "Table 1"),
    Table = replace(Table, which(is.na(Table)), "Table 2")
  ) %>%
  select(Table, Label, everything(), -Variable, -Binary) %>%
  rename(Variable = Label) %>%
  kable(., digits = 3,
        caption = "ANOVA Testing for Continuous Variables Across Site") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"))

```
